I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-27 lipics-master/comppaths.tex
prop 7

\begin{proposition}
	\label{prop.sign}
	${\vx^\star}$ maximizes (${\vx^\sharp}$ minimizes) the value of all positive neurons 
	and minimizes (${\vx^\sharp}$ maximizes) the value of all negative neurons.
\end{proposition}

>>>>

\begin{proposition}
	\label{prop.sign}
	$\max_{\vx} (\val_{\vx} (n)) = \val_{\vx^\star}(n)$ if $S(n)=+1$,
	and $\val_{\vx^\sharp}(n)$ if $S(n)=-1$; and 
	$\min_{\vx} (\val_{\vx} (n)) = \val_{\vx^\sharp}(n)$ if $S(n)=+1$,
	and $\val_{\vx^\star}(n)$ if $S(n)=-1$, for all $n$.
\end{proposition}
